MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-07-19 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\subsection{Community Revenue (Utility)}

The communities and web services earn revenue by performing tasks. The total gain is function of quality of rate of tasks being performed. 
We have adopted a linear equal weight average over all QoS parameters listed in Table \ref{qosws} excluding the $Throughput$ and $Cost$ parameters. A community has the option to weigh specific QoS parameters depending on the expectations of
their clients.

\begin{equation}\label{out_c}
PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
\end{equation}

The revenue function of the web service community is a linear
function of $Out(C)$ with a positive constant multiplier. The
worth of a community is set to the output the community can
generate, i.e., $v(C) = Out(C)$.

>>>>

\subsection{Community Utility}

The communities and web services earn revenue by performing tasks. The total gain is function of quality of rate of tasks being performed.

\begin{equation}\label{out_c}
U_{C} = (Et_{C} - Exp1_{C} - Exp2_{C}) \times Th_{C} \times A_{C}
\end{equation}
